Supporting Information

### 2018-04-02 SupportingInformation.Rmd
adding checkpoint chunk

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
#library(checkpoint)
#---------------------------------------------------------------
#checkloc<-tempdir()
#if (!dir.exists(paste0(checkloc,"/.checkpoint/")))
#{
#  dir.create(paste0(checkloc,"/.checkpoint/"))
#  checkpoint("2018-03-29",checkpointLocation = checkloc)
#}
#---------------------------------------------------------------
#if (!dir.exists("./.checkpoint/")){
#  dir.create("./.checkpoint/")
#}
#checkpoint("2018-03-29",checkpointLocation = "./")
```

>>>>

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```
